% Place acknowledgments below.
A project of this magnitude can not solely be the work of one man, and there are many colleagues I would like to thank and acknowledge for their contributions to this dissertation. First, I am grateful to my advisor, Marcel Salath\'e for his mentoring over the past five years. Of note, I'd like to acknowledge the significant professional opportunities, intelligent conversations, financial support and swiss-made pizza provided. I'd like to thank Charles Fischer, Steven Schaeffer and Kathryn McClintock for their administrative support. I acknowledge the University Health Services for allowing us access to their records, without, chapters 3 and 4 wouldn't exist. I want to thank Tim Leso and Eric Charles for guiding me to do more research in the first two years of my undergraduate degree, starting me out on this crazy path of research. I thank my committee members for the many discussions about this dissertation and their helpful advice. Additionally, I'd like to thank Conrad Tucker for including me into some of his other projects.

I want to thank our group's programmers, Brian Lambert, Issac Bromley, and Shashank Khandelwal, for their work on developing many applications our group has used. I'd also like to thank members of the Open Source Software community that have ever contributed to \LaTeX, Weka, R, Open Office, Python, scikit-learn, GIMP, or were part of the Apache Software Foundation or any of the *nix distributions that I've used during my time as a grad student. I wish that your contributions were more widely acknowledged in academia.

I'd like to thank the Santa Fe Institute for hosting me during the summer of 2013. I'd like to specifically thank Juniper Lovato, John Paul Gonzales, Tom Carter and Sander Bais for organizing the many lectures, networking opportunities, and other events. I'd like to thank Owen Densmore, Stephen Guerin, John Driscoll, Alfred Hubler, David Masad, Mengsen Zhang, Alastair Jamieson-Lane, Nix Barnett, Yan Xu, Carissa Flocken and everyone else that I've met there for the amazing conversations during my time at Santa Fe and after.  

I'd like to thank Susie Lim, Zhuojie Huang, Cosme Adrover, Timo Smieszek, Orhan Kislal, Eun-Kyeong Kim, Spencer Carran, Owen Shartle, Kezia Manlove, Yafei Wang, and Kurt Vandegrift for their various types of support. Finally, I'd like to thank my mother and sister for their continuing support. 
